---
title: "Bright R Shiny Objects"
author: "Rhetta Chappell"
date: "22/01/2021"
output:
  html_document: default
  'html_document runtime: shiny': default
subtitle: Advanced R 2021
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

## Overview:

-   demonstrate how shiny apps, widgets and components can be integrated with .Rmd

    -   Demonstration of inline apps:

      -   shinyApp() function
      
    -   Demonstration of embedding full apps:

      -   using app URL

        -   For more: <https://bookdown.org/yihui/rmarkdown/shiny-documents.html>

-   interactive mapping with leaflet

    -   adding grouped and custom markers to a leaflet map

    -   cluster markers

```{r, echo = FALSE, warning=FALSE, message = FALSE,results="hide"}

################################################################################
################################################################################
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     Load req packages
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
################################################################################
################################################################################
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#    DATA RELATED PACKAGES
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#load packages
suppressPackageStartupMessages({
  #geospatial stuff
  library(rgdal)
  library(maptools)
  library(rgeos)
  library(sp)
  library(sf)
  library(leaflet)
  library(leaflet.providers)
  #data wrangling
  library(data.table)
  library(tidyverse) 
  library(reshape2)
  #library(packrat)
  library(sqldf)
  library(tidyr)
  #text
  #visualisation
  library(plotly)
  library(RColorBrewer)
  library(scales)
  #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  #     SHINY RELATED PACKAGES
  #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  library(shiny)
  library(shinythemes)
  library(shinydashboard)
  library(shinyWidgets)
  library(shinyalert)
  library(shinydashboardPlus)
  library(shinyjqui)
  library(styler)
  library(shinyAce)
  library(shinyEffects)
  library(htmlwidgets)
  library(htmltools)
  library(htmlTable)
  library(shinycssloaders)
})

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     Aesthetic stuff
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
mycol <- colorRampPalette(c("#e30918","#ff8300", "#009736","#00a3ef",
                            "#3b28cc", "#aa9aba")) # IEE & RIDL colours


################################################################################
################################################################################
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     Read in the data
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
################################################################################
################################################################################

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     Spatial Data - 2016 ABS SA2 polygons (shp files) - subset to Logan LGA
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# sa2_log <- readOGR(dsn=path.expand("./Shiny/Code_Slides/data/shape_files"), 
#                    layer="Logan_SA2_2016")

sa2_log <- readOGR(dsn=path.expand("./data/shape_files"), 
                   layer="Logan_SA2_2016")

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     DSS Payments 2020 and ABS Total Population, A & TSI population, Language Spoken at at home 2016 data
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#log_data1 <- read.csv("Shiny/Code_Slides/data/Logan_SA2_DSS2020_Indig_TotalPop_Lang_at_home.csv")
log_data1 <- read.csv("data/Logan_SA2_DSS2020_Indig_TotalPop_Lang_at_home.csv")
#glimpse(log_data1)
log_data1$X<-NULL

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     Merge the df to the spatial data for the map
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
sa2_merged <- raster::merge(sa2_log, log_data1, by = "SA2_NAME16")

```

## Inline apps ShinyApp() \| Leaflet

```{r, echo = FALSE}

shinyApp(
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     UI - what people see and interact with
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  
  ui = fluidPage(
         fluidRow(column(width = 12,  
                  pickerInput("stats_input", 
                  label="Select a data point or statistic to colour the map:",
                  multiple = FALSE,
                  #selected = TRUE,
                  choices = list("# of pop who identify as A & TSI" = "Total_ATSI",
                                "Population" ="Total_pop",
                                "# of Single Parenting Payments (DSS 2020)" = "Parenting_Payment_Single",
                                "# of JobSeeker Payments (DSS 2020)" = "JobSeeker_Payment",
                                "# of Disability Pensions (DSS 2020)" = "Disability_Support_.Pension",
                                "Statistical Area 2 (SA2) 2016" = "SA2_NAME16"
                           ), # end of choices list for stats drop down
                                                                    
                  options = list(`style` = "btn-danger"))#end pickerinput
               )#end column
           ), # end fluidrow
         
         fluidRow(
                column(12,
               # leaflet map output
                 withSpinner(
                    leafletOutput("map",
                                  height = "420px", 
                                  width="100%"))),#end column
                )#end fluid row
            #end fluidRow
         
  ), # endFluidPage
  
  
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     SERVER - back end logic
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  server = function(input, output, session) {
    
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
                                   #MAP OUTPUT 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    #create the base map that will be displayed regardless of selected input
    output$map<-renderLeaflet({
        leaflet(sa2_merged) %>%
            #addProviderTiles(leaflet::providers$Esri.WorldGrayCanvas) %>%
            addProviderTiles(leaflet::providers$Esri.WorldImagery) %>%
            # Centre the map in the middle of our co-ordinates
            fitBounds(152.8, -27.7, 153.3, -27.6)
        
    }) 
    
    
    
    #colour palettes - one numeric one for character or factor vars
    observe({ #beginning of map
        if (input$stats_input == "SA2_NAME16") {
            pal <- colorFactor(mycol(30), 
                               domain= sa2_merged[[input$stats_input]])
        } else {
            pal <- colorNumeric(c("#008B00","#C12525"), 
                                domain = sa2_merged[[input$stats_input]], 
                                reverse = FALSE)
        }
        
        
        
        #labels for polygons - hover or click
        labels <- sprintf(
            "<strong>%s</strong><br/>", 
            sa2_merged$SA2_NAME16) %>% lapply(htmltools::HTML)
        
        #creating a proxy map which reacts to user input
        #displays the various stats from the stats drop down 
        leafletProxy("map", data = sa2_merged) %>%
            clearShapes() %>%
          #add the SA2 polygons, colour and label them
            addPolygons(
                layerId = sa2_merged$SA2_NAME16,
                #colour map polygons based on user input
                #colour pal created above
                fillColor = ~pal(sa2_merged[[input$stats_input]]), 
                #how strong in the fill
                fillOpacity = 0.9,
                #polygon outline weight
                weight = 0.6,
                opacity = 1,
                #outline of polygons
                color = "#FFFFFF",
                dashArray = "2",
                #labels as defined above
                label = labels
            )
        
        
    # creating more human readable legend title based on input
    varname<-switch(input$stats_input,
                     "Total_ATSI" = "# of pop who identify as A & TSI",
                     "Total_pop" = "Population",
                     "Parenting_Payment_Single" = "# of Single Parenting Payments (DSS 2020)",
                     "JobSeeker_Payment" = "# of JobSeeker Payments (DSS 2020)",
                     "Disability_Support_.Pension" = "# of Disability Pensions (DSS 2020)",
                     "SA2_NAME16" = "Statistical Area 2 (SA2) 2016")


    # the proxy map which will display the legend set above
    leafletProxy("map", data = sa2_merged) %>% 
      clearControls() %>%
        addLegend(pal = pal, 
                  opacity = 0.9, 
                  title = varname,
                  values = ~sa2_merged[[input$stats_input]],
                  labels = c(min(input$stats_input), 
                             max(input$stats_input)),
                  position = "topright")
    
    })# end of map shape colour and labeling  and legend observe event
    
  },
  # set height of widget recommended not over 500 px 
  options = list(height = 500, width = "100%")
)# end shinyapp widget 


```

```{r, echo = FALSE, warning=FALSE, message = FALSE,results="hide"}
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     Food outlet data - these data were manually collected by a research assistance Nov 2020
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#food_dat <- read.csv("Shiny/Code_Slides/data/Geocoded_Addresses_Food_Outlet_Logan_Jan_21_2021.csv")
food_dat <- read.csv("data/Geocoded_Addresses_Food_Outlet_Logan_Jan_21_2021.csv")

#unique(food_dat$Outlet_Type)

#recode foot outlet types to consolidate categories
food_dat_types_markers <- food_dat %>% 
    dplyr::select(-X) %>% 
  #consolidate food outlet types as there are way too many
    mutate(Type_Food = case_when(
        Outlet_Type %in% c("Pickup", "Pickup ","Pickup_Delivery","Delivery", 
                           "Restaurant_Takeaway", "Takeaway" ) ~ "Pickup_Delivery",
        Outlet_Type %in% c("Bakery","Bakery " ) ~ "Bakery",
        Outlet_Type %in% c("Convenience_Petrol","Convenience Store", 
                           "Local Market ","Local Market" ) ~ "Local_Convienience",
        Outlet_Type %in% c( "Cafe", "Restaurant", "Restaurant ",
                            "Dessert"  ) ~ "Restaurant_Cafe",
        Outlet_Type %in% c( "Distillery", "Brewery", 
                            "Restaurant_Pub" ) ~ "Pub_Brewery_Distillery",
        Outlet_Type %in% c( "Supermarket ", "Grocery Store",
                            "Butcher" ) ~ "Supermarket",
        Outlet_Type %in% c(  "Water Park ", "Sports Club") ~ "Sports_Club_Park",
        Outlet_Type %in% c("Venue", "Catering" ) ~ "Venue_Catering",
        TRUE ~ as.character(Outlet_Type)
    )) %>% 
  #format names and markers don't like spaces in names
    mutate(Type_Food = gsub(" ", "_", Type_Food),
           Type_Food = as.factor(Type_Food)) %>% 
     #this is a nonsense category of one so get rid of it
    filter(Type_Food != "What_is_is") %>% 
    mutate(Type_Food = factor(Type_Food)) %>%
    glimpse()

levels(food_dat_types_markers$Type_Food)
```

## Adding markers to map \| Geocoded data from Google API

-   custom markers with icons - awesomeIconList(makeAwesomeIcon())
-   group markers based on categorical variable

```{r, echo = FALSE}

shinyApp(
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     UI - what people see and interact with
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  
  ui = fluidPage(
         fluidRow(column(width = 12,  
                  pickerInput("stats_input", 
                  label="Select a data point or statistic to colour the map:",
                  multiple = FALSE,
                  #selected = TRUE,
                  choices = list("# of pop who identify as A & TSI" = "Total_ATSI",
                                "Population" ="Total_pop",
                                "# of Single Parenting Payments (DSS 2020)" = "Parenting_Payment_Single",
                                "# of JobSeeker Payments (DSS 2020)" = "JobSeeker_Payment",
                                "# of Disability Pensions (DSS 2020)" = "Disability_Support_.Pension",
                                "Statistical Area 2 (SA2) 2016" = "SA2_NAME16"
                           ), # end of choices list for stats drop down
                                                                    
                  options = list(`style` = "btn-danger"))#end pickerinput
               )#end column
           ), # end fluidrow
         
         fluidRow(
                column(12,
               # leaflet map output
                 withSpinner(
                    leafletOutput("map",height = "420px", width="100%"))),#end column
                )#end fluid row
            #end fluidRow
         
  ), # endFluidPage
  
  
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     SERVER - back end logic
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  server = function(input, output, session) {
    
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
                                   #MAP OUTPUT 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    #create the base map that will be displayed regardless of selected input
    output$map<-renderLeaflet({
        leaflet(sa2_merged) %>%
            #addProviderTiles(leaflet::providers$Esri.WorldGrayCanvas) %>%
            addProviderTiles(leaflet::providers$Esri.WorldImagery) %>%
            #we only want the markers on the map if the user selects them
            hideGroup(type_group) %>%
            # Centre the map in the middle of our co-ordinates
            fitBounds(152.8, -27.7, 153.3, -27.6)
        
    }) 
    
    
    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    # Create custom Icons - different colour per Brand
    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    # define groups for markers based on categorical variable
    type_group <-levels(food_dat_types_markers$Type_Food)
    
    #what we want the markers to look like when applied to the map
    Food_Icons <- awesomeIconList(
        Hypermarket = makeAwesomeIcon(icon='shopping-cart', library='glyphicon', markerColor = 'black'),
        Supermarket = makeAwesomeIcon(icon='shopping-cart', library='glyphicon', markerColor = 'lightgray'),
        Pickup_Delivery = makeAwesomeIcon(icon='phone', library='glyphicon', markerColor = 'darkblue'),
        Restaurant_Cafe = makeAwesomeIcon(icon='cutlery', library='glyphicon', markerColor = 'cadetblue'),
        Fast_Food_restaurant = makeAwesomeIcon(icon='cutlery', library='glyphicon', markerColor = 'blue'),
        Local_Convienience = makeAwesomeIcon(icon='shopping-cart', library='glyphicon', markerColor = 'gray'),
        Food_relief_service  = makeAwesomeIcon(icon='alert', library='glyphicon', markerColor = 'red'),
        Pub_Brewery_Distillery = makeAwesomeIcon(icon='glass', library='glyphicon', markerColor = 'pink'),
        Bakery = makeAwesomeIcon(icon='grain', library='glyphicon', markerColor = 'beige'),
        Farm = makeAwesomeIcon(icon='apple', library='glyphicon', markerColor = 'green'),
        Food_Manufacturer = makeAwesomeIcon(icon='wrench', library='glyphicon', markerColor = 'orange'),
        Food_Truck = makeAwesomeIcon(icon='bullhorn', library='glyphicon', markerColor = 'purple'),
        Food_Supplier = makeAwesomeIcon(icon='star', library='glyphicon', markerColor = 'lightred'),
        Staff_Exclusive = makeAwesomeIcon(icon='briefcase', library='glyphicon', markerColor = 'lightblue'),
        Sports_Club_Park = makeAwesomeIcon(icon='ok-sign', library='glyphicon', markerColor = 'lightgreen'),
        Supplements_Store = makeAwesomeIcon(icon='map-marker', library='glyphicon', markerColor = 'darkgreen'),
        Venue_Catering = makeAwesomeIcon(icon='ok-sign', library='glyphicon', markerColor = 'darkpurple')
        )
    
    
    
    #colour palettes - one numeric one for character or factor vars
    observe({ #beginning of map
        if (input$stats_input == "SA2_NAME16") {
            pal <- colorFactor(mycol(30), 
                               domain= sa2_merged[[input$stats_input]])
        } else {
            pal <- colorNumeric(c("#008B00","#C12525"), 
                                domain = sa2_merged[[input$stats_input]], 
                                reverse = FALSE)
        }
        
        
        
        #labels for polygons - hover or click
        labels <- sprintf(
            "<strong>%s</strong><br/>", 
            sa2_merged$SA2_NAME16) %>% lapply(htmltools::HTML)
        
        #creating a proxy map which reacts to user input
        #displays the various stats from the stats drop down 
        leafletProxy("map", data = sa2_merged) %>%
            clearShapes() %>%
          #add the SA2 polygons, colour and label them
            addPolygons(
                layerId = sa2_merged$SA2_NAME16,
                #colour map polygons based on user input
                #colour pal created above
                fillColor = ~pal(sa2_merged[[input$stats_input]]), 
                #how strong in the fill
                fillOpacity = 0.9,
                #polygon outline weight
                weight = 0.6,
                opacity = 1,
                #outline of polygons
                color = "#FFFFFF",
                dashArray = "2",
                #labels as defined above
                label = labels)%>% 
            # ADD IN THE MARKERS WE DEFINED ABOVE 
            addAwesomeMarkers(data = food_dat_types_markers,
                          lng = ~lon, lat = ~lat,
                          #control which markers go together when selected
                          group = ~type_group[Type_Food],
                          #what the markers will look like as we set above
                          icon = ~Food_Icons[Type_Food]) %>% 
            #add layer controls - this is how we control the grouping of markers
            addLayersControl(overlayGroups = type_group,
                             options = layersControlOptions(collapsed = FALSE), 
                             position = "bottomright")
        

    
    })# end of map shape colour and labeling  and legend observe event
    
  },
  # set height of widget recommended not over 500 px for slides
  options = list(height = 500, width = "100%")
)# end shinyapp widget 


```

## Clustering markers \| reduce clutter

```{r, echo = FALSE}

shinyApp(
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     UI - what people see and interact with
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  
  ui = fluidPage(
         fluidRow(column(width = 12,  
                  pickerInput("stats_input", 
                  label="Select a data point or statistic to colour the map:",
                  multiple = FALSE,
                  #selected = TRUE,
                  choices = list("# of pop who identify as A & TSI" = "Total_ATSI",
                                "Population" ="Total_pop",
                                "# of Single Parenting Payments (DSS 2020)" = "Parenting_Payment_Single",
                                "# of JobSeeker Payments (DSS 2020)" = "JobSeeker_Payment",
                                "# of Disability Pensions (DSS 2020)" = "Disability_Support_.Pension",
                                "Statistical Area 2 (SA2) 2016" = "SA2_NAME16"
                           ), # end of choices list for stats drop down
                                                                    
                  options = list(`style` = "btn-danger"))#end pickerinput
               )#end column
           ), # end fluidrow
         
         fluidRow(
                column(12,
               # leaflet map output
                 withSpinner(
                    leafletOutput("map",height = "420px", width="100%"))),#end column
                )#end fluid row
            #end fluidRow
         
  ), # endFluidPage
  
  
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#     SERVER - back end logic
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  server = function(input, output, session) {
    
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
                                   #MAP OUTPUT 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    #create the base map that will be displayed regardless of selected input
    output$map<-renderLeaflet({
        leaflet(sa2_merged) %>%
            #addProviderTiles(leaflet::providers$Esri.WorldGrayCanvas) %>%
            addProviderTiles(leaflet::providers$Esri.WorldImagery) %>%
            #we only want the markers on the map if the user selects them
            hideGroup(type_group) %>%
            # Centre the map in the middle of our co-ordinates
            fitBounds(152.8, -27.7, 153.3, -27.6)
        
    }) 
    
    
    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    # Create custom Icons - different colour per Brand
    #~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    # define groups for markers based on categorical variable
    type_group <-levels(food_dat_types_markers$Type_Food)
    
    #what we want the markers to look like when applied to the map
    Food_Icons <- awesomeIconList(
        Hypermarket = makeAwesomeIcon(icon='shopping-cart', library='glyphicon', markerColor = 'black'),
        Supermarket = makeAwesomeIcon(icon='shopping-cart', library='glyphicon', markerColor = 'lightgray'),
        Pickup_Delivery = makeAwesomeIcon(icon='phone', library='glyphicon', markerColor = 'darkblue'),
        Restaurant_Cafe = makeAwesomeIcon(icon='cutlery', library='glyphicon', markerColor = 'cadetblue'),
        Fast_Food_restaurant = makeAwesomeIcon(icon='cutlery', library='glyphicon', markerColor = 'blue'),
        Local_Convienience = makeAwesomeIcon(icon='shopping-cart', library='glyphicon', markerColor = 'gray'),
        Food_relief_service  = makeAwesomeIcon(icon='alert', library='glyphicon', markerColor = 'red'),
        Pub_Brewery_Distillery = makeAwesomeIcon(icon='glass', library='glyphicon', markerColor = 'pink'),
        Bakery = makeAwesomeIcon(icon='grain', library='glyphicon', markerColor = 'beige'),
        Farm = makeAwesomeIcon(icon='apple', library='glyphicon', markerColor = 'green'),
        Food_Manufacturer = makeAwesomeIcon(icon='wrench', library='glyphicon', markerColor = 'orange'),
        Food_Truck = makeAwesomeIcon(icon='bullhorn', library='glyphicon', markerColor = 'purple'),
        Food_Supplier = makeAwesomeIcon(icon='star', library='glyphicon', markerColor = 'lightred'),
        Staff_Exclusive = makeAwesomeIcon(icon='briefcase', library='glyphicon', markerColor = 'lightblue'),
        Sports_Club_Park = makeAwesomeIcon(icon='ok-sign', library='glyphicon', markerColor = 'lightgreen'),
        Supplements_Store = makeAwesomeIcon(icon='map-marker', library='glyphicon', markerColor = 'darkgreen'),
        Venue_Catering = makeAwesomeIcon(icon='ok-sign', library='glyphicon', markerColor = 'darkpurple')
        )
    
    
    
    #colour palettes - one numeric one for character or factor vars
    observe({ #beginning of map
        if (input$stats_input == "SA2_NAME16") {
            pal <- colorFactor(mycol(30), 
                               domain= sa2_merged[[input$stats_input]])
        } else {
            pal <- colorNumeric(c("#008B00","#C12525"), 
                                domain = sa2_merged[[input$stats_input]], 
                                reverse = FALSE)
        }
        
        
        
        #labels for polygons - hover or click
        labels <- sprintf(
            "<strong>%s</strong><br/>", 
            sa2_merged$SA2_NAME16) %>% lapply(htmltools::HTML)
        
        #creating a proxy map which reacts to user input
        #displays the various stats from the stats drop down 
        leafletProxy("map", data = sa2_merged) %>%
            clearShapes() %>%
          #add the SA2 polygons, colour and label them
            addPolygons(
                layerId = sa2_merged$SA2_NAME16,
                #colour map polygons based on user input
                #colour pal created above
                fillColor = ~pal(sa2_merged[[input$stats_input]]), 
                #how strong in the fill
                fillOpacity = 0.9,
                #polygon outline weight
                weight = 0.6,
                opacity = 1,
                #outline of polygons
                color = "#FFFFFF",
                dashArray = "2",
                #labels as defined above
                label = labels)%>% 
            # ADD IN THE MARKERS WE DEFINED ABOVE 
            addAwesomeMarkers(data = food_dat_types_markers,
                          lng = ~lon, lat = ~lat,
                          #control which markers go together when selected
                          group = ~type_group[Type_Food],
                          #what the markers will look like as we set above
                          icon = ~Food_Icons[Type_Food],
                          clusterOptions = markerClusterOptions())
        

    
    })# end of map shape colour and labeling  and legend observe event
    
  },
  # set height of widget recommended not over 500 px for slides
  options = list(height = 500, width = "100%")
)# end shinyapp widget 


```

### Leaflet marker resources:

-   [\<https://github.com/bhaskarvk/leaflet/blob/master/inst/examples/awesomeMarkers.R\>](https://github.com/bhaskarvk/leaflet/blob/master/inst/examples/awesomeMarkers.R){.uri} 

-   [\<https://github.com/rstudio/leaflet/issues/691\>](https://github.com/rstudio/leaflet/issues/691){.uri}  

-   [\<https://getbootstrap.com/docs/3.3/components/\>](https://getbootstrap.com/docs/3.3/components/){.uri}  

-   [\<https://rdrr.io/cran/leaflet/man/makeAwesomeIcon.html\>](https://rdrr.io/cran/leaflet/man/makeAwesomeIcon.html){.uri}  

-   [\<https://rstudio.github.io/leaflet/markers.html\>](https://rstudio.github.io/leaflet/markers.html){.uri}  

### Advanced clustering - custom icons and clusters:

-   [\<https://stackoverflow.com/questions/47507854/coloring-clusters-by-markers-inside\>](https://stackoverflow.com/questions/47507854/coloring-clusters-by-markers-inside){.uri}

## Embedding a full shiny app

```{r}
knitr::include_app("https://regionalinnovationdatalab.shinyapps.io/Logan_Food_Mapping/", 
  height = "700px")
```

